Pitfall of Prediction-orienterd Machine Learning Models and Economic Value of Statistical Efficiency in On-farm Precision Experimentation

### 2022-02-24 Writing/manuscript.rmd
remove the 2880 pictures

---
title: "Pitfall of Prediction-orienterd Machine Learning Methods and Economic Value of Statistical Efficiency in On-farm Precision Experimentation"
author:
  - Taro Mieno^[University of Nebraska Lincoln, tmieno2@unl.edu], Xiaofei Li^[Mississippi State University, xiaofei.li@msstate.edu], David S. Bullock^[University of Illinois, dsbulloc@illinois.edu]
output:
  officedown::rdocx_document:
    toc: false
    toc_depth: 1
    number_sections: true
    reference_docx: "word_template.docx"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: "Figure "
       sep: ": "
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
       style: Table Caption
       pre: "Table "
       sep: ": "
# bibliography: PA.bib
# csl: american-journal-of-agricultural-economics.csl
abstract: ""
---

@@

## Profit performances

@@

```{r yield-curves, fig.cap="Estimated yield response curves at a specific location", fig.height=8.5, fig.width=7, echo=FALSE, cache=FALSE}
include_graphics(here("GitControlled", "Graphs", "802_yield.png"))
```

```{r treatment-effect, fig.cap="", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
include_graphics(here("GitControlled", "Graphs", "treatment_sim_58.png"))
```

>>>>

---
title: "Pitfall of Prediction-orienterd Machine Learning Models and Economic Value of Statistical Efficiency in On-farm Precision Experimentation"
author:
  - Taro Mieno^[University of Nebraska Lincoln, tmieno2@unl.edu], Xiaofei Li^[Mississippi State University, xiaofei.li@msstate.edu], David S. Bullock^[University of Illinois, dsbulloc@illinois.edu]
output:
  officedown::rdocx_document:
    toc: false
    toc_depth: 1
    number_sections: true
    reference_docx: "word_template.docx"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: "Figure "
       sep: ": "
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
       style: Table Caption
       pre: "Table "
       sep: ": "
# bibliography: PA.bib
# csl: american-journal-of-agricultural-economics.csl
abstract: ""
---

@@

### Profit

The production profit of location $i$ by applying the estimated site-specific EONR is:

@@

```{r yield-curves, fig.cap="Estimated yield response curves at a specific location", fig.height=8.5, fig.width=7, echo=FALSE, cache=FALSE}
include_graphics(here("Shared", "Graphs", "802_yield.png"))
```

```{r treatment-effect, fig.cap="", echo=FALSE, fig.height=8.5, fig.width=7, cache=FALSE}
include_graphics(here("Shared", "Graphs", "treatment_sim_58.png"))
```
